 ---
title: "Data Merge"
output: word_document
date: "2025-05-27"
---

To do:


```{r setup}
#| include: FALSE
#| 
knitr::opts_chunk$set(echo = TRUE)

for(packageName in c("here",
                     "magrittr",
#                     "rjson",
                     "tidyjson",
                     "tidyverse")) {
  if(!is.element(packageName,               # If package is NOT installed...
                 installed.packages()[,1])) {
    install.packages(packageName)           #  ...then install it.
  }
  library(packageName,                      # Add package to environment
          character.only=TRUE,
          quietly=TRUE,
          verbose=FALSE)
}

i_am("Scripts/Data Merge.Rmd") # To help find all the files.

options(show.signif.stars = FALSE)          # Don't stargaze
options(digits = 3)                         # Round to 3 digits by default

```

```{r functions}
# # Setup for testing
# ema_df %>%
#   select(starts_with("COPE_Approach_1")) ->
#   df
# # End testing setup

combine_cols <- function(df,                # Data frame
                         item_name) {       # Item Name

  require(tidyverse)
  # Note: For some scales, 0 is a legitimate value, while for others it is
  #  not. Hence, the sort of crazy stuff going on here. This is all to avoid
  #  the problem where the sum of 6 NA should be NA, not 0.
  # This probably only works for the data in its current format, because
  #  there will only be 0 or 1 non-NA values.
  
  # The select seems to stop with the first period, so the next is not
  #  needed.
  # paste(item_name, ".", sep = "") ->
  #   item_name
  
  df %>%
    select(starts_with(paste0(item_name,"."))) ->
    df1

  NA -> df$x
  ncol(df1) ->
    numcol
  
  for(rownum in 1:nrow(df)) {
    if(sum(is.na(df1[rownum,])) != numcol) {
      sum(df1[rownum,],
          na.rm = TRUE) ->
        df$x[rownum]
    }
  }  
  
  str_split(colnames(df1)[1],                # Rename the x column
            "[.]")[[1]][1] ->
    colnames(df)[which(colnames(df) == "x")]

  return(df)
}

# make_key <- function(rsp, 
#                      posix) {
#   
#   vector(mode = "character",
#          length = length(posix_ls)) ->
#     key_vec
#   for(index in 1:length(posix)) {
#     unlist(str_split(posix, "-| |:")) ->
#       posix
# 
#     paste0(rsp, x[1], x[2], x[3], x[4])
#   }
#   
#   lapply(posix,
#          function(x) {
#            paste0(rsp, x[1], x[2], x[3], x[4])
#          }) ->
#     key_ls
#   
#   
#   
#   require(lubridate)
#   str_replace_all(posix,
#                   " UTC",
#                   "") ->
#     posix
#   return(
#     paste0(rsp,
#            lubridate::year(posix),
#            lubridate::month(posix),
#            lubridate::day(posix),
#            lubridate::hour(posix)))
# }
# 

combine_prcs <- function(df) {
  require(tidyverse)
  df %>%
    select(starts_with("PRCS_")) ->
    df
  vector(mode = "character",
         length = nrow(df)) ->
    prcs
  for(index in 1:nrow(df)) {
    if(sum(is.na(df[index,])) != ncol(df)) {
      df[index, which(is.na(df[index,]) == FALSE)] ->
        prcs[index]
    }
  }
  as.numeric(
    unname(
      unlist(prcs))) ->
    prcs
  return(prcs)
}
  
combine_rec <- function(df,
                        n) {
  require(tidyverse)
  df %>%
    select(starts_with("REC_")) %>%
    select(contains(paste0("_",
                           n,
                           "_"))) ->
    df
  vector(mode = "character",
         length = nrow(df)) ->
    rec
  for(index in 1:nrow(df)) {
    if(sum(is.na(df[index,])) != ncol(df)) {
      df[index, which(is.na(df[index,]) == FALSE)] ->
        rec[index]
    }
  }
  unname(
    unlist(rec)) ->
    rec

  return(rec)
}

select_date <- function(df) {
  require(tidyverse)
  
  df %>% 
    select(starts_with("date")) ->
    df1
  
  apply(df1,
        1,
        function(x) 
          min(which(is.na(x) == FALSE))) ->
    dd
  
  rep(NA, nrow(df1)) -> date_vec
  
  for(index in 1:nrow(df1)) {
    unlist(df1[index, dd[index]]) -> date_vec[index]
  }

  as.Date(date_vec) ->
    date_vec

  return(date_vec)
}

select_time <- function(df) {
  require(tidyverse)

  df %>% select(starts_with("ampm")) ->
    df1

  apply(df1,
        1,
        function(x)
          min(which(is.na(x) == FALSE))) ->
    dd

  rep(NA, nrow(df1)) -> time_vec

  for(index in 1:nrow(df1)) {
    unlist(df1[index, dd[index]]) -> time_vec[index]
  }

  return(time_vec)
}

```

# Read Data

## EMA Data

Important notes:

1. Each file has a varying number (and names) of columns, so this is hard coded. 2. Note that the rsp_id limits must be checked as well. Currently the range of valid rsp_id is [64400, 65000] with everything outside that range assumed to be testing entries; the testing entries are removed.

3. All 12 files are stored in a single list, ema_ls. They are NOT joined in any way. The list is stored in here("ema/EMA List.RData").

Still to do: 

```{r read_EMA}
#| echo: FALSE
#| warning: FALSE
#| message: FALSE
#| 

list() -> ema_ls

dir(path = here("ema"),                     # Work in this directory
    pattern = ".csv") -> file_names         # Get the names of all .CSV files

for(index in 1:(length(file_names)/2)) {
  2 * index  -> index2                      # Morning and evening EMA have
  index2 - 1 -> index1                      #  different number of columns
  
  read_csv(file = here(paste0("ema/",
                              file_names[index1])),
           col_select = 1:42) ->
    ema_ls[[index1]]
  NULL -> attr(ema_ls[[index1]], "spec")
  paste0(ema_ls[[index1]]$rsp_id, 
         ema_ls[[index1]]$scheduled_start_local) ->
    ema_ls[[index1]]$key
  as_date(ema_ls[[index1]]$scheduled_start_local) ->
    ema_ls[[index1]]$date
  ifelse(
    str_split_i(ema_ls[[index1]]$scheduled_start_local,
                pattern = " |:",
                i = 2) < 12, "am", "pm") ->
    ema_ls[[index1]]$ampm
  
  
  read_csv(file = here(paste0("ema/",
                              file_names[index2])),
           col_select = 1:46) ->
    ema_ls[[index2]]
  NULL -> attr(ema_ls[[index2]], "spec")
  paste0(ema_ls[[index2]]$rsp_id, 
         ema_ls[[index2]]$scheduled_start_local) ->
    ema_ls[[index2]]$key
  as_date(ema_ls[[index2]]$scheduled_start_local) ->
    ema_ls[[index2]]$date
  ifelse(
    str_split_i(ema_ls[[index2]]$scheduled_start_local,
                pattern = " |:",
                i = 2) < 12, "am", "pm") ->
    ema_ls[[index2]]$ampm
}

lapply(                                     # Remove the testing rsp_id
  ema_ls,    
  function(x) x %>% 
    filter(rsp_id > 64400) %>% 
    filter(rsp_id < 65000)) ->
  ema_ls


unique(                                       # This should be redundant, but
  c(ema_ls[[1]]$mbl_cod, ema_ls[[2]]$mbl_cod, # check it anyway! ema_ls[[1]]
    ema_ls[[3]]$mbl_cod, ema_ls[[4]]$mbl_cod, # should contain them all.
    ema_ls[[5]]$mbl_cod, ema_ls[[6]]$mbl_cod,
    ema_ls[[7]]$mbl_cod, ema_ls[[8]]$mbl_cod,
    ema_ls[[9]]$mbl_cod, ema_ls[[10]]$mbl_cod, 
    ema_ls[[11]]$mbl_cod, ema_ls[[12]]$mbl_cod)) ->
  valid_mobile_codes

save(ema_ls,
     file = here("ema/EMA List.RData"))
```


```{r question_name_checks}
#| eval: FALSE

# Let's make certain all the questions are properly labelled.
# Look through these and compare to the survey creation lists.

c(colnames(ema_ls[[1]]),
  colnames(ema_ls[[2]]),
  colnames(ema_ls[[3]]),
  colnames(ema_ls[[4]]),
  colnames(ema_ls[[5]]),
  colnames(ema_ls[[6]]),
  colnames(ema_ls[[7]]),
  colnames(ema_ls[[8]]),
  colnames(ema_ls[[9]]),
  colnames(ema_ls[[10]]),
  colnames(ema_ls[[11]]),
  colnames(ema_ls[[12]])) ->
  ema_names
table(ema_names)
```

### Data Merging

Now, to merge the EMA data.
```{r}
#| eval: FALSE
# Are the keys unique?

unique(ema_ls[[1]]$key) ->
  keys
for(index in 2:12) {
  c(keys, unique(ema_ls[[index]]$key)) ->
    keys
}

length(keys) == length(unique(keys))
# If the preceding is TRUE, then all keys are unique

```

Step 1: Join all the data frames, using a complex key (rsp_id + date + hour)
```{r}
full_join(ema_ls[[1]],
          ema_ls[[2]],
          by = join_by(key)) ->
  ema_df

3 -> index
index + 1 -> index

for(index in 3:12) {
  full_join(ema_df,
            ema_ls[[index]],
            by = join_by(key)) ->
    ema_df
}

ema_df[ , order(names(ema_df))] ->
  ema_df

```

Step 2: Combine items where appropriate. This can be done by rowSums(., na.rm = TRUE)

There's an issue with combine_cols(): MSPSS_1 matches MSPSS_1, MSPSS_10, etc.
Fix that one! (Issue on 1 July 2025)

```{r}
# There's a better way to do this, I'm sure. However, this is quick and doesn't
#  require much thinking about enquote, assign, etc, so it will save me time.
combine_cols(ema_df, "mbl_cod") -> ema_df
combine_cols(ema_df, "rsp_id") -> ema_df
combine_cols(ema_df, "instance_id") -> ema_df
select_date(ema_df) -> ema_df$date
select_time(ema_df) -> ema_df$ampm
combine_cols(ema_df, "timezone_offset") -> ema_df

combine_cols(ema_df, "COPE_1") -> ema_df
combine_cols(ema_df, "COPE_2") -> ema_df
combine_cols(ema_df, "COPE_3") -> ema_df
combine_cols(ema_df, "COPE_4") -> ema_df
combine_cols(ema_df, "COPE_5") -> ema_df
combine_cols(ema_df, "COPE_6") -> ema_df

combine_cols(ema_df, "CSET_1") -> ema_df
combine_cols(ema_df, "CSET_2") -> ema_df
combine_cols(ema_df, "CSET_3") -> ema_df
combine_cols(ema_df, "CSET_4") -> ema_df
combine_cols(ema_df, "CSET_5") -> ema_df
combine_cols(ema_df, "CSET_6") -> ema_df
combine_cols(ema_df, "CSET_7") -> ema_df
combine_cols(ema_df, "CSET_8") -> ema_df
combine_cols(ema_df, "CSET_9") -> ema_df

combine_cols(ema_df, "LSEQ_Restlessness") -> ema_df
combine_cols(ema_df, "LSEQ_Wakefulness") -> ema_df

combine_cols(ema_df, "MSPSS_1") -> ema_df
combine_cols(ema_df, "MSPSS_2") -> ema_df
combine_cols(ema_df, "MSPSS_3") -> ema_df
combine_cols(ema_df, "MSPSS_4") -> ema_df
combine_cols(ema_df, "MSPSS_5") -> ema_df
combine_cols(ema_df, "MSPSS_6") -> ema_df
combine_cols(ema_df, "MSPSS_7") -> ema_df
combine_cols(ema_df, "MSPSS_8") -> ema_df
combine_cols(ema_df, "MSPSS_9") -> ema_df
combine_cols(ema_df, "MSPSS_10") -> ema_df
combine_cols(ema_df, "MSPSS_11") -> ema_df
combine_cols(ema_df, "MSPSS_12") -> ema_df

combine_cols(ema_df, "PANASSF_1") -> ema_df
combine_cols(ema_df, "PANASSF_2") -> ema_df
combine_cols(ema_df, "PANASSF_3") -> ema_df
combine_cols(ema_df, "PANASSF_4") -> ema_df
combine_cols(ema_df, "PANASSF_5") -> ema_df
combine_cols(ema_df, "PANASSF_6") -> ema_df
combine_cols(ema_df, "PANASSF_7") -> ema_df
combine_cols(ema_df, "PANASSF_8") -> ema_df
combine_cols(ema_df, "PANASSF_9") -> ema_df
combine_cols(ema_df, "PANASSF_10") -> ema_df
combine_cols(ema_df, "PANASSF_11") -> ema_df
combine_cols(ema_df, "PANASSF_12") -> ema_df
combine_cols(ema_df, "PANASSF_13") -> ema_df
combine_cols(ema_df, "PANASSF_14") -> ema_df
combine_cols(ema_df, "PANASSF_15") -> ema_df
combine_cols(ema_df, "PANASSF_16") -> ema_df
combine_cols(ema_df, "PANASSF_17") -> ema_df
combine_cols(ema_df, "PANASSF_18") -> ema_df
combine_cols(ema_df, "PANASSF_19") -> ema_df
combine_cols(ema_df, "PANASSF_20") -> ema_df

combine_cols(ema_df, "PROMIS_3A_1") -> ema_df
combine_cols(ema_df, "PROMIS_8A_1") -> ema_df

combine_cols(ema_df, "PSQ_1") -> ema_df
combine_cols(ema_df, "PSQ_2") -> ema_df
combine_cols(ema_df, "PSQ_3") -> ema_df
combine_cols(ema_df, "PSQ_4") -> ema_df
combine_cols(ema_df, "PSQ_5") -> ema_df
combine_cols(ema_df, "PSQ_6") -> ema_df
combine_cols(ema_df, "PSQ_7") -> ema_df
combine_cols(ema_df, "PSQ_8") -> ema_df

combine_cols(ema_df, "PTGISF_1") -> ema_df
combine_cols(ema_df, "PTGISF_2") -> ema_df
combine_cols(ema_df, "PTGISF_3") -> ema_df
combine_cols(ema_df, "PTGISF_4") -> ema_df
combine_cols(ema_df, "PTGISF_5") -> ema_df
combine_cols(ema_df, "PTGISF_6") -> ema_df
combine_cols(ema_df, "PTGISF_7") -> ema_df
combine_cols(ema_df, "PTGISF_8") -> ema_df
combine_cols(ema_df, "PTGISF_9") -> ema_df
combine_cols(ema_df, "PTGISF_10") -> ema_df

combine_cols(ema_df, "ROE_1") -> ema_df
combine_cols(ema_df, "ROE_2") -> ema_df
combine_cols(ema_df, "ROE_3") -> ema_df
combine_cols(ema_df, "ROE_4") -> ema_df
combine_cols(ema_df, "ROE_5") -> ema_df
combine_cols(ema_df, "ROE_6") -> ema_df

ema_df %>%                                  # Remove the detritus created by
  select(!ends_with("x")) %>%               #  the joins.
  select(!ends_with("y")) ->
  ema_df

```

Fix particular missingness:

- For many EMA items, a value of "-9" indicates missingness.
- For LSEQ items, a value of "-1" indicates missingness. (Not yet fixed; 1 July 2025. Waiting on confirmation from Alex.)
```{r}
NA ->                                       # Skipped 1 or more EMA: COPE, CSET,
  ema_df[ema_df == -9]                      #  MSPSS, PSQ, PANAS, PTGI, ROE
NA ->                                       # Skipped LSET question(s)
  ema_df[ema_df == -1]
  
```

```{r}

# These are done here to avoid the NA problem in the previous chunk.
combine_rec(ema_df,1) -> ema_df$REC1
combine_rec(ema_df,2) -> ema_df$REC2
combine_prcs(ema_df) -> ema_df$PRCS

ema_df %>%                                  # Remove the detritus created by
  select(!starts_with("PRCS_")) %>%
  select(!starts_with("REC_")) ->
  ema_df

```

Check the data integrity: Are there any data outside the scale range?

```{r check_ema_values}

# These should all return integer(0) if the data meet the integrity check.

apply(
  ema_df %>%
    select(starts_with("COPE")),
  2,
  function(x) which(x > 3 | x < 0))         # COPE scale range: [0,3]

apply(
  ema_df %>%
    select(starts_with("CSET")),
  2,
  function(x) which(x > 7 | x < 1))         # CSET scale range: [1,7]

apply(
  ema_df %>%
    select(starts_with("LSEQ")),
  2,
  function(x) which(x > 100 | x < 0))

apply(
  ema_df %>%
    select(starts_with("MSPSS")),
  2,
  function(x) which(x > 7 | x < 1))

apply(
  ema_df %>%
    select(starts_with("PANASSF")),
  2,
  function(x) which(x > 5 | x < 1))

apply(
  ema_df %>%
    select(starts_with("PROMIS")),
  2,
  function(x) which(x > 5 | x < 1))

apply(
  ema_df %>%
    select(starts_with("PSQ")),
  2,
  function(x) which(x > 4 | x < 1))

apply(
  ema_df %>%
    select(starts_with("PTGI")),
  2,
  function(x) which(x > 5 | x < 0))

apply(
  ema_df %>%
    select(starts_with("ROE")),
  2,
  function(x) which(x > 5 | x < 1))

```


Step 3: Put the subscale designation into the column names. (E.g. A column name of "PSQ_1" becomes "PSQ_Demands_1" and so on.)
```{r}

colnames(ema_df) ->
  ema_names

str_replace_all(ema_names, "COPE_1" ,"COPE_Active_1") ->
  ema_names
str_replace_all(ema_names, "COPE_2" ,"COPE_Accept_2") ->
  ema_names
str_replace_all(ema_names, "COPE_3" ,"COPE_Support_3") ->
  ema_names
str_replace_all(ema_names, "COPE_4" ,"COPE_Venting_4") ->
  ema_names
str_replace_all(ema_names, "COPE_5" ,"COPE_Disengage_5") ->
  ema_names
str_replace_all(ema_names, "COPE_6" ,"COPE_SelfBlame_6") ->
  ema_names
str_replace_all(ema_names, "PSQ_1" ,"PSQ_Demands_1") ->
  ema_names
str_replace_all(ema_names, "PSQ_2" ,"PSQ_NoJoy_2") ->
  ema_names
str_replace_all(ema_names, "PSQ_3" ,"PSQ_Tension_3") ->
  ema_names
str_replace_all(ema_names, "PSQ_4" ,"PSQ_Worries_4") ->
  ema_names
str_replace_all(ema_names, "PSQ_5" ,"PSQ_Worries_5") ->
  ema_names
str_replace_all(ema_names, "PSQ_6" ,"PSQ_NoJoy_6") ->
  ema_names
str_replace_all(ema_names, "PSQ_7" ,"PSQ_Tension_7") ->
  ema_names
str_replace_all(ema_names, "PSQ_8" ,"PSQ_Demands_8") ->
  ema_names
str_replace_all(ema_names, "MSPSS_1" ,"MSPSS_SigOth_1") ->
  ema_names
str_replace_all(ema_names, "MSPSS_2" ,"MSPSS_SigOth_2") ->
  ema_names
str_replace_all(ema_names, "MSPSS_3" ,"MSPSS_Family_3") ->
  ema_names
str_replace_all(ema_names, "MSPSS_4" ,"MSPSS_Family_4") ->
  ema_names
str_replace_all(ema_names, "MSPSS_5" ,"MSPSS_SigOth_5") ->
  ema_names
str_replace_all(ema_names, "MSPSS_6" ,"MSPSS_Friends_6") ->
  ema_names
str_replace_all(ema_names, "MSPSS_7" ,"MSPSS_Friends_7") ->
  ema_names
str_replace_all(ema_names, "MSPSS_8" ,"MSPSS_Family_8") ->
  ema_names
str_replace_all(ema_names, "MSPSS_9" ,"MSPSS_Friends_9") ->
  ema_names
str_replace_all(ema_names, "MSPSS_10" ,"MSPSS_SigOth_10") ->
  ema_names
str_replace_all(ema_names, "MSPSS_11" ,"MSPSS_Family_11") ->
  ema_names
str_replace_all(ema_names, "MSPSS_12" ,"MSPSS_Friends_12") ->
  ema_names
str_replace_all(ema_names, "PANASSF_1" ,"PANASSF_Positive_1") ->
  ema_names
str_replace_all(ema_names, "PANASSF_2" ,"PANASSF_Negative_2") ->
  ema_names
str_replace_all(ema_names, "PANASSF_3" ,"PANASSF_Positive_3") ->
  ema_names
str_replace_all(ema_names, "PANASSF_4" ,"PANASSF_Negative_4") ->
  ema_names
str_replace_all(ema_names, "PANASSF_5" ,"PANASSF_Positive_5") ->
  ema_names
str_replace_all(ema_names, "PANASSF_6" ,"PANASSF_Negative_6") ->
  ema_names
str_replace_all(ema_names, "PANASSF_7" ,"PANASSF_Negative_7") ->
  ema_names
str_replace_all(ema_names, "PANASSF_8" ,"PANASSF_Negative_8") ->
  ema_names
str_replace_all(ema_names, "PANASSF_9" ,"PANASSF_Positive_9") ->
  ema_names
str_replace_all(ema_names, "PANASSF_10" ,"PANASSF_Positive_10") ->
  ema_names
str_replace_all(ema_names, "PANASSF_11" ,"PANASSF_Negative_11") ->
  ema_names
str_replace_all(ema_names, "PANASSF_12" ,"PANASSF_Positive_12") ->
  ema_names
str_replace_all(ema_names, "PANASSF_13" ,"PANASSF_Negative_13") ->
  ema_names
str_replace_all(ema_names, "PANASSF_14" ,"PANASSF_Positive_14") ->
  ema_names
str_replace_all(ema_names, "PANASSF_15" ,"PANASSF_Negative_15") ->
  ema_names
str_replace_all(ema_names, "PANASSF_16" ,"PANASSF_Positive_16") ->
  ema_names
str_replace_all(ema_names, "PANASSF_17" ,"PANASSF_Positive_17") ->
  ema_names
str_replace_all(ema_names, "PANASSF_18" ,"PANASSF_Negative_18") ->
  ema_names
str_replace_all(ema_names, "PANASSF_19" ,"PANASSF_Positive_19") ->
  ema_names
str_replace_all(ema_names, "PANASSF_20" ,"PANASSF_Negative_20") ->
  ema_names
str_replace_all(ema_names, "PTGISF_1" ,"PTGISF_Life_1") ->
  ema_names
str_replace_all(ema_names, "PTGISF_2" ,"PTGISF_Life_2") ->
  ema_names
str_replace_all(ema_names, "PTGISF_3" ,"PTGISF_Possible_3") ->
  ema_names
str_replace_all(ema_names, "PTGISF_4" ,"PTGISF_Strength_4") ->
  ema_names
str_replace_all(ema_names, "PTGISF_5" ,"PTGISF_Spirit_5") ->
  ema_names
str_replace_all(ema_names, "PTGISF_6" ,"PTGISF_Relate_6") ->
  ema_names
str_replace_all(ema_names, "PTGISF_7" ,"PTGISF_Possible_7") ->
  ema_names
str_replace_all(ema_names, "PTGISF_8" ,"PTGISF_Relate_8") ->
  ema_names
str_replace_all(ema_names, "PTGISF_9" ,"PTGISF_Relate_9") ->
  ema_names
str_replace_all(ema_names, "PTGISF_10" ,"PTGISF_Strength_10") ->
  ema_names
str_replace_all(ema_names, "PTGISF_11" ,"PTGISF_Possible_11") ->
  ema_names
str_replace_all(ema_names, "PTGISF_12" ,"PTGISF_Strength_12") ->
  ema_names
str_replace_all(ema_names, "PTGISF_13" ,"PTGISF_Life_13") ->
  ema_names
str_replace_all(ema_names, "PTGISF_14" ,"PTGISF_Possible_14") ->
  ema_names
str_replace_all(ema_names, "PTGISF_15" ,"PTGISF_Relate_15") ->
  ema_names
str_replace_all(ema_names, "PTGISF_16" ,"PTGISF_Relate_16") ->
  ema_names
str_replace_all(ema_names, "PTGISF_17" ,"PTGISF_Possible_17") ->
  ema_names
str_replace_all(ema_names, "PTGISF_18" ,"PTGISF_Spirit_18") ->
  ema_names
str_replace_all(ema_names, "PTGISF_19" ,"PTGISF_Strength_19") ->
  ema_names
str_replace_all(ema_names, "PTGISF_20" ,"PTGISF_Relate_20") ->
  ema_names
str_replace_all(ema_names, "PTGISF_21" ,"PTGISF_Relate_21") ->
  ema_names

ema_names ->
  colnames(ema_df)

```

Step 4: Create instance means for each scale. Can't use totals because there are different number of items for some subscales am and pm.

LSET and PROMIS are single items, so no averaging is needed.
```{r}

ema_df %>%
  mutate(PANAS_PA = rowMeans(across(contains("_Positive_")),
                                    na.rm = TRUE)) %>%
  mutate(PANAS_NA = rowMeans(across(contains("_Negative_")),
                             na.rm = TRUE)) %>%
  mutate(CSET = rowMeans(across(contains("CSET")),
                         na.rm = TRUE)) %>%
  mutate(PTGI_Relate = rowMeans(across(contains("_Relate_")),
                                na.rm = TRUE)) %>%
  mutate(PTGI_Life = rowMeans(across(contains("_Life_")),
                              na.rm = TRUE)) %>%
  mutate(PTGI_Strength = rowMeans(across(contains("_Strength_")),
                                  na.rm = TRUE)) %>%
  mutate(PSQ_Demands = rowMeans(across(contains("_Demands_")),
                                na.rm = TRUE)) %>%
  mutate(PSQ_Worries = rowMeans(across(contains("_Worries_")),
                                na.rm = TRUE)) %>%
  mutate(PSQ_Tension = rowMeans(across(contains("_Tension_")),
                                na.rm = TRUE)) %>%
  mutate(PSQ_NoJoy = rowMeans(across(contains("_NoJoy_")),
                              na.rm = TRUE)) %>%
  mutate(ROE = rowMeans(across(starts_with("ROE")),
                        na.rm = TRUE)) %>%
  mutate(MSPSS_SigOth = rowMeans(across(contains("_SigOth_")),
                                 na.rm = TRUE)) %>%
  mutate(MSPSS_Family = rowMeans(across(contains("_Family_")),
                                 na.rm = TRUE)) %>%
  mutate(MSPSS_Friends = rowMeans(across(contains("_Friends_")),
                                  na.rm = TRUE)) ->
  # mutate(COPE_Approach = rowMeans(across(contains("_Approach_")),
  #                                 na.rm = TRUE)) %>%
  # mutate(COPE_Avoid = rowMeans(across(contains("_Avoid_")),
  #                              na.rm = TRUE)) ->
  ema_df

save(ema_df,
     file = here("EMA df.RData"))

```

Step 5: Make long? Do something?
```{r}

```

## Audio
BTW, the audio files have names something like this:
aud_9891105_1732744605.m4a
The "1732744605" is the instance ID in EMA data. Each can be found in the corresponding mbl_cod folder under the audio folder.

There are 2 formats for the audio data; M4A and 3GG. These appear to be from IOS and Android phones, respectively. Will that matter?

It is impractical to put the audio data into a list; that list would be huge. Hence, all analyses will be done reading in the data using the ID.

We'll ignore the extra (almost empty) folders; if the folder isn't in valid_mobile_codes, then it gets ignored.

For some potential analyses, see: Schultebraucks, K., Yadav, V., Shalev, A. Y., Bonanno, G. A., & Galatzer-Levy, I. R. (2022). Deep learning-based classification of posttraumatic stress disorder and depression following trauma utilizing visual and auditory markers of arousal and mood. Psychological Medicine, 52(5), 957–967. https://doi.org/10.1017/S0033291720002718

Chip also indicates that these would be helpful audio analyses: ????
 
```{r audio}
#| echo: FALSE
#| eval: FALSE
#| 
dir(here("audio")) ->
  audio_dir
audio_dir[which(!(dir(here("audio")) %in% keep_codes))] ->
  del_dir
paste0("audio/",
       del_dir) ->
  del_sub_dir

unlink(x = del_sub_dir[1],
       recursive = TRUE)

```

## Fitbit Biomarkers

```{r hrvExample}
#| include: FALSE
#| eval: FALSE
tidyjson::read_json(
  path = here("../IRIS Data Backup/fitbit_data/2025-05-03.json"),
  format = "json") -> 
  test1

# The next gives a list of 76 entries (the last 380 (=76 x 5) minutes of
#  2025-05-03) for the IRIS1002 watch.
#
# JSON is a strange format. Just roll with the first part of this list
#  access:
test1[[2]][[1]]$IRIS1002$hrv[[1]]$hrv

# The entries look like this (for the 75th interval of the sequence, and with
#  explanations interspersed).

# [[1]]$minutes[[75]]
# [[1]]$minutes[[75]]$minute
# [1] "2025-05-03T23:50:00.000"
# - timestamp: the start of the 5 minutes interval for which the following 
# values were computed


# [[1]]$minutes[[75]]$value
# [[1]]$minutes[[75]]$value$rmssd
# [1] 20
# - rmssd: "root mean square of successive differences" - the square root of 
# the mean of the squares of the successive differences between adjacent
# beat-to-beat intervals

# [[1]]$minutes[[75]]$value$coverage        #
# [1] 0.911
# - coverage: the number of data points in the interval, multiplied by the 
# mean beat-to-beat of the interval in seconds and divided by the number of
# seconds in the interval (300 seconds)

# [[1]]$minutes[[75]]$value$hf
# [1] 112
# - high_frequency: measures short term variations in heart rate and captures
# parasympathetic activity

# [[1]]$minutes[[75]]$value$lf
# [1] 716
# - low_frequency: measures long term variations in heart rate and reflects
# activity from both the sympathetic and parasympathetic branches

# test1[[2]][[1]]$IRIS1002$hrv[[2]]$hrv gives the previous day (2025-05-02);
#  there are 92 entries there, of the same format as above. And so on.




test1[[2]][[1]]$IRIS1002$heart[[1]] -> dum1


test1[[2]][[1]]$IRIS1002$heart[[1]]$`activities-heart-intraday` -> dum1


# Here are all the heartrate data.
length(test1[[2]][[1]]$IRIS1002$heart[[1]]$`activities-heart-intraday`$dataset)

# > test1[[2]][[1]]$IRIS1002$heart[[2]]$requested_date
# [1] "2025-05-02"
# > test1[[2]][[1]]$IRIS1002$heart[[1]]$requested_date
# [1] "2025-05-03"
# > test1[[2]][[1]]$IRIS1002$heart[[3]]$requested_date
# [1] "2025-05-01"
# > test1[[2]][[1]]$IRIS1002$heart[[4]]$requested_date
# [1] "2025-04-30"
# > test1[[2]][[1]]$IRIS1002$heart[[5]]$requested_date
# [1] "2025-04-29"
# > test1[[2]][[1]]$IRIS1002$heart[[6]]$requested_date
# [1] "2025-04-28"
# > test1[[2]][[1]]$IRIS1002$heart[[7]]$requested_date
# [1] "2025-04-27"
# > test1[[2]][[1]]$IRIS1002$heart[[8]]$requested_date

```

Pull of IRIS2002$hrv for all of the data that have them.

```{r IRIS1002_test}
sort(
  dir(path = here("fitbit_data"),
      pattern = ".json")) ->
  fitbit_files

list() ->
  hrv_ls ->
  data_ls

0 -> data_index
for(index in 1:length(fitbit_files)) {
  tidyjson::read_json(path = paste0(here("fitbit_data",fitbit_files[index])),                         format = "json")[[2]][[1]] -> 
    data1
  if("IRIS1002" %in% names(data1)) {
    data1$IRIS1002$hrv ->         # 
      hrv_ls[[index]]
#print(index)
    if(length(hrv_ls[[index]]) > 0) {       #
#print(length(hrv_ls[[index]]))
      for(index2 in 1:length(hrv_ls[[index]])) {
        if(length(hrv_ls[[index]][[index2]]) > 0) {
#print(names(hrv_ls[[index]][[index2]]))
          if("hrv" %in% names(hrv_ls[[index]][[index2]])) {
            unname(unlist(hrv_ls[[index]][[index2]]$hrv)) ->
              hrv1
            if(is.null(hrv1) == FALSE) {
              #
              # Need to check data formats. If the first element can be cast
              #  to a date, drop it.
              # Because there may be error, need a try-catch
              #
              tryCatch(
                {
                  suppressWarnings(
                    is.Date(as.Date.character(hrv1[1])))
                },
                error = function(cond) {
                  FALSE
                },
                warning = function(cond) {
                  FALSE
                }
                finally = function(cond) {
                  TRUE
                }
              )
              1 + data_index ->
                data_index
              t(matrix(hrv1[-1],
                       nrow = 5,
                       ncol = (length(hrv1)-1)/5)) ->
                data_ls[[data_index]]
            }
            # Merge data_ls elements into a data frame
            #
            # Still need to convert first column to Date + time
            # Still need to convert columns 2:5 from character to numeric
            #
            # Remove duplicate data (if any exist)
            #
          }
        }
      }
    }
  }
}



```


```{r}
log_calculator <- function(x){
    tryCatch(
        expr = {
            message(log(x))
            message("Successfully executed the log(x) call.")
        },
        error = function(e){
            message('Caught an error!')
            print(e)
        },
        warning = function(w){
            message('Caught an warning!')
            print(w)
        },
        finally = {
            message('All done, quitting.')
        }
    )    
}

log_calculator(2)
log_calculator(-2)

```


# Joins

