---
title: "Transcribing"
output: word_document
date: "2025-05-27"
---

This expects the following folder structure.

Project Folder (any name and any location; I use "Benight - IRIS")
 +- audio
 |- Scripts
 
 This file must live in the "Scripts" folder.
 The IRIS.Rproj file must be in the project folder.
 All of the audio files are in the audio folder, each in its own folder (associated with the mobile code).

```{r setup}
#| include: FALSE
#| 
knitr::opts_chunk$set(echo = TRUE)

for(packageName in c("av", 
                     "devtools", 
                     "here",
                     "magrittr",
                     "parallelly",
#                     "purrr",
                     "tidyverse")) {
  if(!is.element(packageName,               # If package is NOT installed...
                 installed.packages()[,1])) {
    install.packages(packageName)           #  ...then install it.
  }
  library(packageName,                      # Add package to environment
          character.only=TRUE,
          quietly=TRUE,
          verbose=FALSE)
}

i_am("Scripts/Transcribing.Rmd") # To help find all the files.

options(show.signif.stars = FALSE)          # Don't stargaze
options(digits = 3)                         # Round to 3 digits by default


# You may need to do some additional installs (e.g., Rtools) before the
#  next one works. (Or you may already have those on your system.)
# If prompted to update, choose "1" to update all files.
#
# See: https://github.com/bnosac/audio.whisper for more information

# The next requires some external tools to run properly. Hence, be prepared
#  for some work to get this installed.
if(!is.element("audio.whisper",
               installed.packages()[,1])) {
  if(packageVersion("audio.whisper") != "0.5.0") {
    devtools::install_github("bnosac/audio.whisper",
                             force = TRUE)
  }
}

library(audio.whisper)
```

# Audio

BTW, the audio files have names something like this:

aud_9891105_1732744605.m4a

The "1732744605" is the instance ID in EMA data. All audio files can be found in the corresponding mbl_cod folder under the audio folder.

There are 2 formats for the audio data; M4A and 3GP. These appear to be from IOS and Android phones, respectively.

There are many extra folders; the ones without audio get ignored.

## Get the File List
```{r fileList}
c(
  dir(path = here(),
      pattern = "m4a",
      recursive = TRUE),                    # Look in the subfolders
  dir(path = here(),
      pattern = "3gp",
      recursive = TRUE)) ->
  audio_file_names

```

Only process the new names

- Read in all the old names
```{r}
dir(path = here("audio"),                   # These are all the transcriptions.
    pattern = ".RData",
    recursive = TRUE) ->                    # Look in the subfolders
transcript_names

read_csv(here("audio/Bad Names.csv")) ->    # These are known bad files
  bad_names_df

#
# Do we need to switch from a data frame here?
#

vector(mode = "character") ->
  audio_to_skip

for(transcript in transcript_names) {       # For each transcription
  load(here("audio", transcript))           # Load transcript & file names
  
  c(audio_to_skip,                          # Combine the file names in that
    unlist(transcription_data$names)) ->    #  transcript with the other bad
    audio_to_skip                           #  or completed file names
}

audio_file_names[!(audio_file_names %in% audio_to_skip)] ->
  audio_file_names

# This has no effect...why, I wonder...
audio_file_names[!(audio_file_names %in% bad_names_df$name)] ->
  audio_file_names

```

## Prep for Transcription

 Also, note that whisper() can use GPU with a parameter in trans() (NVidia and Metal; the latter is on my MacMini.)

```{r whisperPrep}
#| include: FALSE
# This chunk takes some time, but it stores the result and only calls up the
#  stored file after it has been created.
#
# The newest version of audio.whisper (0.5.0) has more, and apparently faster, 
#  models. However, installation will take some fudging (must cmake) right now
#  (as of 2026-02-15, it isn't on CRAN).
#
# Might be sufficient to use the "medium" model; it would be much faster.

  whisper("large-v3-turbo") ->              # Smaller models take less time.
    model2                                  #  Roughly 40% faster than large-v2

```


## Transcribe

```{r processAudio}

#length(audio_file_names)
#rm(list = "transcriptions_ls")

list() ->
  transcriptions_ls
list() ->
  audio_ls
# I have about enough memory to a bunch at a time. (Each one takes about
#  10 MB.) Just to be careful, I do 1:500, then 501:1000, then 1001:1500, etc.
#  Check the length of audio_file_names to know the maximum to go to.
# These take a while, though; about 60 files per hour get done. Need
#  to make this an incremental thing after the first one.
#
# 2026-01-30: audio_file_name[368] has a glitch, so skip that one for now.
#  Others have glitches, too, so those are left out. Those that are left out
#  will be apparent from the names of the saved files.
# 
# Something happens around 1234. I dunno what, but there is a run of bad
#  files.
#
#
# Ah...be very careful: It was possible that the next could overwrite an 
#  existing set of data. Hence, append the date to the name.
1 -> start_index
167 -> end_index                          # 167 today (2026-02-23)

for(index in start_index:end_index) {
  audio_file_names[index] ->
    file_name
  print(paste(index, "-",                   # Keeping track
              Sys.time()))
  
  unlist(                                   # Do we want to index anything?
    strsplit(x = file_name,                 #  Could split only on the period,
             split = "[_./]+")) ->          #  but there may be reasons to
    name_parts                              #  use the other parts later.

  if(name_parts[6] == "m4a") {              # Convert iOS audio
    av_audio_convert(
      audio = here(file_name),
      format = "WAV",                       # Required for whisper
      sample_rate = 16000,                  # Required for whisper
      output = here("temp.wav"),
      verbose = FALSE)
  } 
  if(name_parts[6] == "3gp") {              # Convert Android audio
    av_audio_convert(
      audio = here(file_name),
      format = "WAV",                       # Required for whisper
      sample_rate = 16000,                  # Required for whisper
      output = here("temp.wav"),
      verbose = FALSE)
  }

  capture.output(                           # Don't show all the output.
    predict(object = model2,                 # Transcribe
            newdata = here("temp.wav"),     # temp audio file
            language = "en",                # English
            n_threads = availableCores()) -># Use multiple threads if possible.
    transcriptions_ls[[index]])             # Store with information
  file_name -> audio_ls[[index]]
}

list("names" = audio_ls,
     "transcripts" = transcriptions_ls) ->
  transcription_data
save(transcription_data,
     file = here(paste0("audio/Transcripts ",
                        start_index,
                        " - ",
                        end_index,
                        " - ",
                        Sys.Date(),
                        ".RData")))

```

```{r bad_files}

# First Time Through
# c(400, 772, 1156, 1160, 1196, 1302, 1304,
#   1306, 1307, 1310, 1311, 1312, 1313, 1314,
#   1315, 1318, 1319, 1321, 1322, 1323, 1342,
#   1634, 1638, 1651, 1659, 1667, 1731) ->
#   bad_nums
# 
# data.frame(
#   name = audio_file_names[bad_nums]) ->
#   bad_names
# 
# write_csv(bad_names,
#           file = here("audio/Bad Names.csv"))


# After First Time Through, run this part:
c() ->           # Fill in any bad numbers here
  bad_nums

read_csv(here("audio/Bad Names.csv")) ->
  bad_names

c(bad_names$names,
  audio_file_names[bad_nums]) ->
  bad_names$names

write_csv(bad_names,
          file = here("audio/Bad Names.csv"))

```


## Miscellaneous notes

The transcription output, when using large-v3-turbo:



For some other potential analyses, see: Schultebraucks, K., Yadav, V., Shalev, A. Y., Bonanno, G. A., & Galatzer-Levy, I. R. (2022). Deep learning-based classification of posttraumatic stress disorder and depression following trauma utilizing visual and auditory markers of arousal and mood. Psychological Medicine, 52(5), 957–967. https://doi.org/10.1017/S0033291720002718

Chip also indicates that there are analyses he would like done.

Jenna ran transcripts through [LiWC](https://www.liwc.app)

PyPi SpeechRecognition may be useful. However, we may be able to do it in R:

- https://rpubs.com/Ian_M/919060
- https://reintech.io/blog/voice-recognition-with-r-guide-for-developers (especially the seewave package)
- https://reintech.io/blog/speech-recognition-with-r-tutorial
- package:voice
- https://stackoverflow.com/questions/77710695/trying-to-transcribe-audio-files-in-r
- https://www.r-bloggers.com/2025/11/readtextgrid-now-uses-c-and-chatgpt-helped

Following this post seems to work:
https://www.bnosac.be/index.php/blog/105-audio-transcription-with-whisper-from-r

Some of the data files are quite noisy; they perhaps should be low-pass filtered or de-hissed before processing, but it doesn't seem to be a problem yet.

Conversions with the large model takes much longer than the medium model, which in turn takes about 20 times as long as the tiny model. Is it worth it? I don't know (b/c I haven't investigated it yet.)


```{r speedtest}
#| eval: FALSE
Sys.time()
  capture.output(                           # Don't show all the output.
    predict(object = model,                 # Transcribe w/ large-v2
            newdata = here("temp.wav"),     # temp audio file
            language = "en",                # English
            n_threads = availableCores()) -># Use multiple threads if possible.
    trans1)             # Store with information
Sys.time()
  capture.output(                           # Don't show all the output.
    predict(object = model2,                # Transcribe w/ large-v3-turbo
            newdata = here("temp.wav"),     # temp audio file
            language = "en",                # English
            n_threads = availableCores()) -># Use multiple threads if possible.
    trans2)             # Store with information
Sys.time()

```